Experiment 1 Analysis

### 2023-07-21 Analysis/data_organize.qmd
numeric description table
Cleanup/organize
count n tables

```{r}
pacman::p_load(tidyverse,lme4,emmeans,here,knitr,kableExtra)
options(dplyr.summarise.inform=FALSE)
d <- readRDS(here("data/dPrune-05-21-23.rds")) %>% ungroup()
d$stage <- factor(d$stage, ordered=TRUE, levels = c("1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23"))
d$tOrder <- factor(d$tOrder, levels=c("testFirst","trainFirst"),labels=c("Test First","Train First"))
d$bandOrder <- factor(d$catOrder,levels=c("orig","rev"),labels=c("Original","Reverse"))
d$fb <- factor(d$fb,levels=c("continuous","ordinal"),labels=c("Continuous","Ordinal"))

@@

@@

@@

>>>>

```{r}
pacman::p_load(tidyverse,lme4,emmeans,here,knitr,kableExtra,reactable)
options(dplyr.summarise.inform=FALSE)
d <- readRDS(here("data/dPrune-05-21-23.rds")) %>% ungroup()
d$stage <- factor(d$stage, ordered=TRUE, levels = c("1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23"))
d$tOrder <- factor(d$tOrder, levels=c("testFirst","trainFirst"),labels=c("Test First","Train First"))
d$bandOrder <- factor(d$catOrder,levels=c("orig","rev"),labels=c("Original","Reverse"))
d$fb <- factor(d$fb,levels=c("continuous","ordinal"),labels=c("Continuous","Ordinal"))

@@

```{r}
d %>% select_if(is.numeric) |> colnames()
```

@@

```{r}

d %>%
  distinct(id, condit, fb, bandOrder, tOrder) %>%
  group_by(condit, fb, bandOrder, tOrder) %>%
  summarise(n = n()) %>%
  kable()
```

```{r}

# Average trials per subject by condition  
d %>%
  group_by(condit, fb, bandOrder, tOrder, id) %>%
  summarise(n = n()) %>%
  group_by(condit, fb, bandOrder, tOrder) %>%
  summarise(mean_trials = mean(n)) %>%
  kable()

d %>%
  group_by(condit, fb, bandOrder, tOrder, id, expMode) %>% 
  summarise(n = n()) %>%
  pivot_wider(names_from = expMode, values_from = n, names_prefix = "n_") %>%
  group_by(condit, fb, bandOrder, tOrder) %>%
  summarise(across(starts_with("n_"), ~mean(., na.rm = TRUE))) %>%
  kable()

@@

```{r}
#| column: page-right
#| 
# Define column defs function 
col_defs <- function(data) {

  cols <- colnames(data)

  defs <- lapply(cols, function(x) {

    if(is.factor(data[[x]])) {
      colDef(sortable = TRUE, filterable = TRUE,minWidth=108) 
    } else {
      colDef(sortable = TRUE, filterable = FALSE,minWidth=90)
    }

  })

  setNames(defs, cols)
}

d %>%
  group_by(id,condit, fb, bandOrder, tOrder, expMode) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = expMode, values_from = n, names_prefix = "n_") %>%

  # Pass original data too 
  reactable(columns = col_defs(.), 
            highlight = TRUE,
            defaultPageSize = 25)
```

```{r}

### 2023-07-21 Analysis/e1_Analysis.qmd
count n tables

@@

```
```{r}

df <- data.frame(level = c("a", "b", "c", 'd'), outcome = c(2.3, 1.9, 3.2, 1))

ggplot(df) +
  geom_col_pattern(
    aes(level, outcome, pattern_fill = level), 
    pattern = 'stripe',
    fill    = 'white',
    colour  = 'black'
  ) +
  theme_bw(18) +
  theme(legend.position = 'none') + 
  labs(
    title    = "ggpattern::geom_col_pattern()",
    subtitle = "pattern = 'stripe'"
  ) +
  coord_fixed(ratio = 1/2)

ggplot(e1) +
  geom_col_pattern(
    aes(vb, vx, pattern_fill = bandType), 
    pattern = 'stripe',
    fill    = 'white',
    colour  = 'black'
  ) +
  theme_bw(18) +
  theme(legend.position = 'none') + 
  labs(
    title    = "ggpattern::geom_col_pattern()",
    subtitle = "pattern = 'stripe'"
  ) +
  coord_fixed(ratio = 1/2)
```

>>>>

### Dictionary

@@
